---
title: "Mosaic Integration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mosaic Integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MosaicNMF)
library(RcppML)
```
Generate random data
```{r data}
testList = MosaicNMF::getTestData()
```

Scale each dataset so that each modality contribute equally
```{r}
for (i in 1:length(testList)){
  testList[[i]] = MosaicNMF::scaleDataset(testList[[i]])
}
```

Stack matrix using list of data and filling missing values with 0
```{r}
a_mat = MosaicNMF::stackMatrix(dataList = testList,missingValue=0)
a_mat
```

Generate a matrix indicating the location of missing values to be imputed
```{r}
missingValues = MosaicNMF::getMissingIndices(testList)

missingValues = MosaicNMF::getMaskMatrix(
  missingRows = missingValues$rowCoord,
  missingColumns = missingValues$colCoord,
  dim = "row",
  numRow = MosaicNMF:::getTotalRows(testList),
  numCol = length(MosaicNMF:::getUniqueCells(testList))
  )
```

Determine the most optimal rank using cross validation on randomly masked values
```{r}
res= MosaicNMF::crossValidateWithMissingValues(data=a_mat,k=1:10,missingValues = missingValues)

nplot = MosaicNMF::plotCV(res)
nplot
```

Once you have determined the best rank. Use RcppML to perform NMF at rank 8
```{r}
m <- RcppML::nmf(a_mat, 8, mask = missingValues)
```

To impute all missing values. Perform W*H
```{r}
A_hat = m@w %*% m@h
```

